\title{Cover Letter Master}
\author{Aswath Subramanian}
\date{May 2024}

\documentclass[a4paper,11pt]{letter}
\usepackage[default]{sourcesanspro}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{fontawesome}  % Font awesome icons
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage[hidelinks]{hyperref}


% Set the page margins
\geometry{a4paper, top=4cm, bottom=3cm, left=2.5cm, right=2.5cm}

% Setup the header
\pagestyle{fancy}
\fancyhf{} % clear all header fields
\fancyhead[L]{
    {\large \textbf{Achmadi, S.T, M.T}}\\
    {\faHome}  Keputih Gg.2 no 27/B, Sukolilo, Surabaya\\
    {\faEnvelopeO} \href{mailto:mekatronik.achmadi@gmail.com} mekatronik.achmadi@gmail.com\\
    {\faPhone} +62-812-54274855
    }
\fancyhead[R]{\textbf{\today}}
\medskip\vspace*{1pt}

%%%%%%  LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Recipient address - Optional.
%\noindent
%\large \textbf{Recipient Name}\\ \small Position or Title\\ \small Company Name\\ \small Company Address\\ \small City, State, ZIP
%\medskip

%Salutation
\normalsize Dear Hiring Manager,

% Letter body
\small \noindent
I am writing to express my interest in the amazing opportunity for the Firmware Engineer position at Synapsis Sinergi Digital.
I believe my experience makes me an adaptable candidate for this position within your organization.

\vspace{1pt}
I have experience in research and development as a designer and programmer in embedded systems in academic environments.
I have built several prototypes based on multiple chips and implementing various standards.
My favorite activities is programming chips using RTOS, like ChibiOS/RT on STM32 or ESP-IDF on ESP32, from a GNU/Linux computer.
Not only chip programming, I also enjoy design my own PCBs using KiCAD.
My favorite programming language is C, C++, and Python.
I also willing to learn new system languages such as Rust.


\vspace{1pt}
I am excited about the opportunity to contribute and to take on new challenges that will help me grow both personally and professionally.
I am confident that my experience would be an asset to your organization, and I would welcome the opportunity to discuss my qualifications further.

\bigskip
\noindent
Best regards,\\
\textbf{Achmadi}

\end{document}
